---
title: "2025-09-15_p8130-homework-01"
author: "Chris"
date: "2025-09-15"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
---


# Problem 2

## Prepare the Data
Create two vectors.
```{r}
vec_ls = c(12, 15, 10, 14, 13, 16, 20, 18, 9, 11, 17, 19, 14, 13, 15)

vec_os = c(20, 25, 22, 30, 18, 27, 24, 21, 29, 26, 22, 23, 28, 24)
```

## Question a
```{r}
ls_mean = mean(vec_ls)
ls_median = median(vec_ls)
ls_range = range(vec_ls)
ls_sd = sd(vec_ls)

ls_mean
ls_median
ls_range
ls_sd
```

The mean of recovery time for the laparoscopic group is **`r ls_mean`**, median is
**`r ls_median`**, the minimum is **`r min(vec_ls)`**, the maximum is **`r max(vec_ls)`** and standard deviation is **`r ls_sd`**.

## Question b
```{r drawing a boxplot}
boxplot(vec_ls,
        main = "Recovery Time for LS Group",
        ylab = "Days",
        col = "yellow",
        border = "black"
        )
```

## Question c
```{r}
os_mean = mean(vec_os)
os_median = median(vec_os)
os_range = range(vec_os)
os_sd = sd(vec_os)

os_mean
os_median
os_range
os_sd
```
The mean of recovery time for the laparoscopic group is **`r os_mean`**, median is
**`r os_median`**, the minimum is **`r min(vec_os)`**, the maximum is **`r max(vec_os)`** and standard deviation is **`r os_sd`**.

## Question d
```{r}
boxplot(vec_os,
        main = "Recovery Time for OS Group",
        ylab = "Days",
        col = "lightblue",
        border = "black"
        )
```

## Question e
Combine two vectors into a single list.
```{r}
data_whole = list("col_ls" = vec_ls, "col_os" = vec_os)

boxplot(data_whole,
        main = "Recovery Time by Type",
        ylab = "Days",
        col = c("pink", "lightgreen"),
        border = "black")
```













